\begin{enumerate}
\item Cards bearing numbers $2, 3, 4, \ldots, 11$ are kept in a bag. A card is drawn at random from the bag. The probability of getting a card with a prime number is\\
\begin{enumerate}
\item $\frac{1}{2}$\\
\item $\frac{2}{5}$\\
\item $\frac{3}{10}$\\
\item $\frac{5}{9}$\\
\end{enumerate}
%Probability
\item A card is drawn at random from a well shuffled pack of $52$ cards. Find the probability of getting\\
\begin{enumerate}[label=\Roman*.]
\item a red king.\\
\item a queen or a jack.\\
\end{enumerate}
%Probability
\item All kings, queens and aces are removed from a pack of $52$ cards. The remaining cards are well shuffled and then a card is drawn from it. Find the probability that the drawn card is \\
\begin{enumerate}[label=\Roman*.]
\item a black face card.\\
\item a red card.\\
\end{enumerate}
%probability
\item Two dices are thrown together. The probability of getting the same number on both dices is :\\
\begin{enumerate}
\item $\frac{1}{2}$\\
\item $\frac{1}{3}$\\
\item $\frac{1}{6}$\\
\item $\frac{1}{12}$\\
\end{enumerate}
%probability
\item A number is selected at random from first $50$ natural numbers. Find the probability that it is a multiple of $3$ and $4$.\\
%probability
\item A box contains $100$ red cards, $200$ yellow cards and $50$ blue cards. If a card is drawn at random from the box, then find the probability that it will be \begin{enumerate}[label=\Roman*.]
\item a blue card
\item not a yellow card
\item neither a yellow nor a blue card.\\
\end{enumerate}
\item The probability of a non-leap year having $53$ Mondays is \\
\begin{enumerate}
\item $\frac{2}{7}$\\
\item $\frac{1}{7}$\\
\item $\frac{5}{7}$\\
\item $\frac{6}{7}$\\
\end{enumerate}
\item A child has a die whose six faces show the letters as given below :\\
The die is thrown once. Find the probability of getting\\
\begin{enumerate}[label=\Roman*.]
\item A\\
\item D\\
\end{enumerate}
\item Cards marked with numbers $1,3,5, \ldots, 101$ are placed in a bag and mixed thoroughly. A card is then drawn at random from the bag. Find the probability that the number on the drawn card is 
\begin{enumerate}[label=\Roman*.]
\item less than $19$.
\item a prime number less than $20$.\\
\end{enumerate}
\end{enumerate}
